animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-30 animbook-journal.Rmd
last check before ETC5543 submission

  This animation was developed using two software based on JavaScript, D3.js (@d3js), and WebGL (reference). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins. For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (@r).

@@

  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (@ggplot2) to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. This includes `gifski_renderer()` from the \CRANpkg{gifski} package {@gifski} to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package {@av} to save it into a video file format.

@@

In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation. The initial step is to reformat the data to the animated data structure as seen in \@ref(fig:data-diagram). The second stage is creating a `ggplot` object, which can be subsequently passed into the animation function. The final step involves transforming the `ggplot` to a `gganimate` object by integrating the animation settings. This three-step structure was implemented to ensure that users, regardless of their level of experience, can produce the animations with simplicity while retaining customization for more experienced users.

@@

```{r tbl-animprep}
argument_table |> 
  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaline")) |> 
  knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
```

@@

This paper is created using the \CRANpkg{rjtools} packages (@rjtools) and is based on the 0.0.0.9 version of the \pkg{animbook} package. This version is available on [GitHub](https://github.com/KrisanatA/animbook).

I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar and spelling.

>>>>

  This animation was developed using the software based on JavaScript, D3.js (@d3js), and WebGL (@webgl). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins. For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (@r).

@@

  The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (@ggplot2) to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of `transition_*()` functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. This includes `gifski_renderer()` from the \CRANpkg{gifski} package (@gifski) to save animation in GIF format or `av_renderer()` from the \CRANpkg{av} package (@av) to save it into a video file format.

@@

In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation. The initial step is to reformat the data to the animated data structure as seen in Figure \@ref(fig:data-diagram). The second stage is creating a `ggplot` object, which can be subsequently passed into the animation function. The final step involves transforming the `ggplot` to a `gganimate` object by integrating the animation settings. This three-step structure was implemented to ensure that users, regardless of their level of experience, can produce the animations with simplicity while retaining customization for more experienced users.

@@

```{r tbl-animprep}
argument_table |> 
  filter(argument %in% c("ngroup", "breaks", "group_scaling", "scaling")) |> 
  knitr::kable(caption = "The argument in the anim\\_prep for customized the data scaling.")
```

@@

This paper is created using the \CRANpkg{rjtools} packages (@rjtools) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper. This paper is based on the 0.0.0.9 version of the \pkg{animbook} package. This version is available on [GitHub](https://github.com/KrisanatA/animbook). 
I also acknowledge the use of ChatGPT (https://chat.openai.com/) to improve the text, grammar, and spelling.

- The presentation for the ETC5543 can be found on [GitHub.](https://github.com/KrisanatA/animbook-presentation)
- This paper is contained in the following [GitHub repository.](https://github.com/KrisanatA/animbook-journal)

### 2023-10-30 animbook-journal.tex
last check before ETC5543 submission

This animation was developed using two software based on JavaScript, D3.js (Bostock (2012)), and WebGL (reference). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins. For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (R Core Team (2021)).

@@

The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (Wickham (2016)) to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package \{Ooms (2023b)\} to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package \{Ooms (2023a)\} to save it into a video file format.

@@

In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation. The initial step is to reformat the data to the animated data structure as seen in \ref{fig:data-diagram}. The second stage is creating a \texttt{ggplot} object, which can be subsequently passed into the animation function. The final step involves transforming the \texttt{ggplot} to a \texttt{gganimate} object by integrating the animation settings. This three-step structure was implemented to ensure that users, regardless of their level of experience, can produce the animations with simplicity while retaining customization for more experienced users.

@@

\caption{\label{tab:tbl-animprep}The argument in the anim\_prep for customized the data scaling.}
\centering
\begin{tabular}[t]{l|l}
\hline
Argument & Description\\
\hline
ngroup & The number of groups or categories to create for scaling values.\\
\hline
breaks & A vector of breaks for creating bins.\\
\hline
group\_scaling & The column name that represents the grouping variable.\\
\hline
\end{tabular}
\end{table}

@@

\begin{verbatim}
#> # A tibble: 10 x 5
#>    id     time qtile frame color
#>    <fct> <int> <dbl> <dbl> <fct>
#>  1 1      2020     5     2 X    
#>  2 1      2023     5     3 X    
#>  3 2      2020     5    20 X    
#>  4 2      2023     5    21 X    
#>  5 3      2020     5    34 X    
#>  6 3      2023     5    35 X    
#>  7 4      2020     5    20 X    
#>  8 4      2023     5    21 X    
#>  9 5      2020     5    45 X    
#> 10 5      2023     5    46 X
\end{verbatim}

@@

\begin{verbatim}
#> List of 2
#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
#>   ..$ frame: num [1:400] 2 3 20 21 34 35 20 21 45 46 ...
#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
#>  $ settings:List of 7
#>   ..$ gap           : num 0.1
#>   ..$ xbreaks       : int [1:2] 2020 2023
#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ time_dependent: logi FALSE
#>   ..$ runif_min     : num 1
#>   ..$ runif_max     : num 50
#>  - attr(*, "class")= chr "animbook"
\end{verbatim}

@@

This paper is created using the \CRANpkg{rjtools} packages (O'Hara-Wild et al. (2023)) and is based on the 0.0.0.9 version of the \pkg{animbook} package. This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.

I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar and spelling.

@@

>>>>

This animation was developed using the software based on JavaScript, D3.js (Bostock (2012)), and WebGL (Mozilla Foundation (2011)). The D3 JavaScript is one of the most widely known libraries for creating an interactive and dynamic visualization. It enables the designers to bind both the data and graphical elements to the DOM (Document Object Model). On the other hand, WebGL functions as a JavaScript API for rendering interactive 2D and 3D graphics within any compatible web browser without the use of plug-ins. For the animation in this paper, the programming language that will be used for recreating and revising the visualization done by The New York Times articles is R (R Core Team (2021)).

@@

The \CRANpkg{gganimate} package is an extension from the \CRANpkg{ggplot2} package (Wickham (2016)) to include the description of an animation. It added new grammar classes to the plot object, allowing it to understand how the plot should change over time. The use of \texttt{transition\_*()} functions allows it to achieve this by specifying how the data evolves and how it relates to itself across time. This includes \texttt{gifski\_renderer()} from the \CRANpkg{gifski} package (Ooms (2023b)) to save animation in GIF format or \texttt{av\_renderer()} from the \CRANpkg{av} package (Ooms (2023a)) to save it into a video file format.

@@

In designing the \pkg{animbook} package, a three-step structured approach was developed to create an animation. The initial step is to reformat the data to the animated data structure as seen in Figure \ref{fig:data-diagram}. The second stage is creating a \texttt{ggplot} object, which can be subsequently passed into the animation function. The final step involves transforming the \texttt{ggplot} to a \texttt{gganimate} object by integrating the animation settings. This three-step structure was implemented to ensure that users, regardless of their level of experience, can produce the animations with simplicity while retaining customization for more experienced users.

@@

\caption{\label{tab:tbl-animprep}The argument in the anim\_prep for customized the data scaling.}
\centering
\begin{tabular}[t]{l|l}
\hline
Argument & Description\\
\hline
ngroup & The number of groups or categories to create for scaling values.\\
\hline
breaks & A vector of breaks for creating bins.\\
\hline
group\_scaling & The column name that represents the grouping variable.\\
\hline
scaling & The scaling method to be used; "rank" or "absolute."\\
\hline
\end{tabular}
\end{table}

@@

\begin{verbatim}
#> # A tibble: 10 x 5
#>    id     time qtile frame color
#>    <fct> <int> <dbl> <dbl> <fct>
#>  1 1      2020     5    36 X    
#>  2 1      2023     5    37 X    
#>  3 2      2020     5    49 X    
#>  4 2      2023     5    50 X    
#>  5 3      2020     5    48 X    
#>  6 3      2023     5    49 X    
#>  7 4      2020     5    50 X    
#>  8 4      2023     5    51 X    
#>  9 5      2020     5    43 X    
#> 10 5      2023     5    44 X
\end{verbatim}

@@

\begin{verbatim}
#> List of 2
#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
#>   ..$ frame: num [1:400] 36 37 49 50 48 49 50 51 43 44 ...
#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
#>  $ settings:List of 7
#>   ..$ gap           : num 0.1
#>   ..$ xbreaks       : int [1:2] 2020 2023
#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ time_dependent: logi FALSE
#>   ..$ runif_min     : num 1
#>   ..$ runif_max     : num 50
#>  - attr(*, "class")= chr "animbook"
\end{verbatim}

@@

This paper is created using the \CRANpkg{rjtools} packages (O'Hara-Wild et al. (2023)) and utilized the \CRANpkg{dplyr}, \CRANpkg{knitr}, \CRANpkg{gganimate}, and \CRANpkg{kableExtra} for creating the visual included in this paper. This paper is based on the 0.0.0.9 version of the \pkg{animbook} package. This version is available on \href{https://github.com/KrisanatA/animbook}{GitHub}.
I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar, and spelling.

\begin{itemize}
\tightlist
\item
  The presentation for the ETC5543 can be found on \href{https://github.com/KrisanatA/animbook-presentation}{GitHub.}
\item
  This paper is contained in the following \href{https://github.com/KrisanatA/animbook-journal}{GitHub repository.}
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-webgl}{}}%
Mozilla Foundation. 2011. {``WebGL.''} Khronos WebGL Working Group. \href{https://www.khronos.org/webgl/}{www.khronos.org/webgl/}.
